Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-04 src/paper.tex
update

\subsection{Modeling}
\begin{figure}
\centering
\includegraphics[width=0.35\textwidth]{assets/cross_attention.pdf}
\caption{Overview of TSELM.}
\label{cross_attention}
\end{figure}
\subsubsection{Attention Embedding}
After obtaining the discrete tensor \(\bm{d}\) with shape \(n\times T\), we use 6
learnable embedding tables each with \(K\) entires to embed the 6 layers 
respectively, each resulting in a tensor of shape \(T \times E\). 
After embedding, we follow the same recipe as in \cite{dasb} to 
aggregate the tensor by using attention mechanism to sum all the 6 tensors. This summation 
keeps the information of each layer while reducing the system complexity by reducing the 
dimension of layers.

\subsubsection{Cross Attention}
One of the key factors in target speaker extraction is to 
inject the information of target speaker 
into the mixture. Spex+ \cite{spex_plus} jointly trains a speaker verification task module 
besides the separator, which might not be optimal for the separator task \cite{sef_net}. SEF-Net \cite{sef_net} has proposed an speaker embedding free way to inject the 
target speaker information into the mixture by using cross attention module, and it has 
achieved superior performance compared to other methods. Therefore, we apply 
the cross attention module to inject the reference embedding into the mixture.

>>>>

\subsection{Modeling}
\begin{figure}
\centering
\includegraphics[width=0.35\textwidth]{assets/cross_attention.pdf}
\caption{Details of Cross Attention mechanism.}
\label{cross_attention}
\end{figure}
\subsubsection{Attention Embedding}
After obtaining the discrete tensor \(\bm{d}\) with shape \(n\times T\), we use 6
learnable embedding tables each with \(K\) entires to embed the 6 layers 
respectively, each resulting in a tensor of shape \(T \times E\). 
After embedding, we follow the same recipe as in \cite{dasb} to 
aggregate the tensor by using attention mechanism to sum all the 6 tensors. This summation 
keeps the information of each layer while reducing the system complexity by reducing the 
dimension of layers. After attention embedding, we obtain reference embedding \(E_r\) and 
mixture embedding \(E_m\).

\subsubsection{Cross Attention}
One of the key factors in target speaker extraction is to 
inject the information of target speaker 
into the mixture. Spex+ \cite{spex_plus} jointly trains a speaker verification task module 
besides the separator, which might not be optimal for the separator task \cite{sef_net}. SEF-Net \cite{sef_net} has proposed an speaker embedding free way to inject the 
target speaker information into the mixture by using cross attention module, and it has 
achieved superior performance compared to other methods. Therefore, we apply 
the cross attention module to inject the reference embedding into the mixture. The details 
are in Fig.\ref{cross_attention}.
The cross attention module consists of a positional 
embedding layer, a cross-multiple head attention module, 
and a FiLM module. 
We use \(E_m\) as query and \(E_r\) as key and value for 
the attention module. The output of the cross-multiple head attention module \(E_{spk}\)
is passed together with \(E_m\) to get the final output of the module.
